### 2020-02-04 Literature Review/Literature Review - Revised/.history/sections/DynMARL_20200204152650.tex
Added Chapter 8

    This suggestion aims to build upon the work presented by Hu et al. \cite{Hu2019} in which the
    point is made that the vast majority of the work done in this area considers games with a finite
    (usually two) number of agents. This limits the capability of the analysis to generalise to much
    larger agent populations, such as swarms. To allieviate this concern, the authors present an
    anaysis of the learning dynamics for a large agent population (which they approximate as
    containing infinite agents) where each agent is an independent Q-Learning using Boltzmann
    exploration. The emergent dynamics is given by a Fokker-Planck equation which is numerical shown
    to be a strong approximation of the true learning dynamics. However, as the authors point out,
    this is the first attempt at considering such a problem, and relies on heavy assumptions.
    Possible extensions therefore require a consideration of asymmetic games, stateful games (which
    ties in to Section \ref{sec::Stateful}) and heterogenous populations.

@@

>>>>

    This suggestion aims to build upon the work presented by Hu et al. \cite{Hu2019} in which the
    point is made that the vast majority of the work done in this area considers games with a finite
    (usually two) number of agents. This limits the capability of the analysis to generalise to much
    larger agent populations, such as swarms. To allieviate this concern, the authors present an
    anaysis of the learning dynamics for a large agent population (which they approximate as
    containing infinite agents) where each agent is an independent Q-Learning using Boltzmann
    exploration. The emergent dynamics is given by a Fokker-Planck equation which is numerical shown
    to be a strong approximation of the true learning dynamics. However, as the authors point out,
    this is the first attempt at considering such a problem, and relies on heavy assumptions.
    Possible extensions therefore require a consideration of:

    \begin{itemize}
        \item Asymmetric games, in which agents have different payoffs, introducing heterogeneity
        and competition into the system.
        \item Stateful Games.
        \item Heterogeneous populations, in which there are p different populations of agents.
    \end{itemize}

    To the best of my knowledge, in the particular case of $N >> 1$ agent populations, none of the
    above have yet been attempted.

@@

    \cite{Amato2015PlanningUncertainty}

### 2020-02-04 Literature Review/Literature Review - Revised/sections/DynMARL.tex
Added Chapter 8

    This is potentially the most relevant of the sections in regards to applicability to
    reinforcement learning as it extends the typical consideration of stateless normal-form games,
    in which the payoffs and strategies of each player is well defined, to stochastic games, in
    which games have probabilistic transitions across them. I have yet to explore this section in
    depth.

@@

    \cite{Amato2015PlanningUncertainty}

>>>>

    This is potentially the most relevant of the sections in regards to direct applicability to
    reinforcement learning as it extends the typical consideration of stateless normal-form games,
    in which the payoffs and strategies of each player is well defined, to stochastic games, in
    which games have probabilistic transitions across them. To the best of my knowledge, the
    existing work in this area is sparse. The earliest example is proposed by Vrancx et al 
    \cite{Vrancx2008} in which the authors extend the concept of replicator dynamics to 'piecewise
    replicator dynamics', which allows them to consider multi-state games with discrete transitions
    between them. However, this analysis places strong assumptions on the nature of the learning, in
    particular that, at each state, the strategies in all other states may be considered as fixed.
    Whilst the authors attempt to add corrections to mitigate this effect, it is clear from the
    results that the lack of state-coupling produces deficiencies in the accuracy of the model.
    Hennes et al \cite{Hennes2009} improve upon this result by incorporating state-coupling into the
    model, leading to 'state-coupled replicator dynamics'. This is proven to be a stronger indicator
    of the behaviour of their chosen learning algorithm (the Linear Reward Inaction Penalty put
    forward by Bowling and Veloso \cite{LRI}). Hennes et al. \cite{Hennes2010} go on to use the
    state-coupled replicator dynamics to reverse-engineer a learning automata algorithm, known as
    RESQ-Learning, which is shown to arrive at desired pure or Nash equilibria.

    The state-coupled replicator dynamics provides an important step into the advancement of
    Dynamical Studies of Multi Agent Learning. However, the above appear to be the only works
    presented in this area and so its improvement is an open area of study. Potential directions for
    this include:

    \begin{itemize}
        \item The consideration of larger state spaces (the above studies only consider two).
        \item Lifting the assumption of ergodicity on the state space
        \item Extending the results to extensive form games. The closest attempt to this is
        considered by Panozzo et al. \cite{Panozzo} who consider Q-Learning in a sequence form game.
    \end{itemize}

@@

    To this end, the potential avenue for research in this regard is to extend the ideas of Sanders
    et al. and Galla et al. towards games learnt using classical reinforcement learning algorithms 
    (such as Q-Learning with Boltzmann exploration, which seems to be a common choice). The work may
    then be able to extend beyond this, and towards continuous spaces, stateful games and large
    agent populations. This would allow for an understanding of the important parameters which
    define the behaviour of reinforcement learning algorithms and allow for a characterisation of
    the expected resultant behaviour when applying a particular algorithm to a particular game. It
    would also allow for a characterisation of the conditions under which MARL algorithms may
    feasibly be applied, thereby supporting the ability of researchers and engineers to choose their
    payoff matrices and parameters accordingly.
